Title here

### 2017-01-03 portfolio/text/ms.Rmd
Clean up

<!-- Papers to cite [@smith1986] -->

@@

<!-- TODO: cut apart and recombine the following couple chunks:-->

@@

<!-- Chakravorty, U. and Nemoto, K. (2001) Modeling the effects of area closure
and tax policies: a spatial-temporal model of the hawaii longline fishery.
Marine Resource Economics 15, 179–204.

Costello C, Gaines SD, Lynham J (2008) Can catch shares prevent fisheries
collapse? Science 321(5896):1678–1681

Crowder, L.B. and Murawski, S.A. (1998) Fisheries bycatch: implications for
management. Fisheries Management 23, 8–17.

Curtis, R. and Hicks, R.L. (2000) The Cost of sea turtle preservation: the case
of Hawaii’s Pelagic longliners. American Journal of Agricultural Economics 82,
1191– 1197.

Hilborn R, Ovando D. 2014 Reflections on the success of traditional fisheries
management. ICES J. Mar. Sci. 71, 1040–1046.

Lewison, R.L., Crowder, L.B., Rimprove fishing gear ead, A.J. and Freeman, S.A.
(2004) Understanding impacts of fisheries bycatch on marine megafauna. Trends in
Ecology & Evolution 19, 598–604.

Read, A.J., Drinker, P. and Northridge, S. (2006) Bycatch of marine mammals in
US and global fisheries. Conservation Biology 20, 163–169. -->

<!-- Reconciling the different levels of effects -->

<!--In terrestrial agriculture for instance, there are many instances of
specializing being profitable; drivers include the ability to specialize on
high-profit cash crops (tobacco, cocoa), the availability of government
agricultural subsidies (soybeans, corn in the USA), and farming on a large
industrial scale (REF).-->

<!-- Limitations + obvious extensions paragraph -->

<!-- ### Implications for limited entry, ITQs, and catch shares -->

<!-- - concerning because in many areas of the world and fisheries, regulations and -->
<!--   market forces have encouraged specialization / limited (effective) -->
<!--   diversification (e.g. multiple permits or diverse permits) -->

<!-- - locking into permits limits ability to pick lower risk strategies and is -->
<!--   getting people locked into low diversity permits that may be doing well now, -->
<!--   but not necessarily always -->

@@

External market forces may interact in concert with management regulations to
promote specialization for fishers or other individuals dependent on natural
resources. With increasing environmental variability and extreme events in
a changing climate (REF), it is particularly important that individuals who rely
on natural resources as a primary source of income have strategies to reduce
risk. Though variability in individual revenue may not be actively incorporated
into many management decisions, analyses like ours help to understand the range
of diversification strategies available and how their benefits may change over
time.

@@

<!-- # Notes -->

<!-- ## @kasperski2013 -->
<!-- - vessel-level CFEC data -->
<!-- - dome-shaped result -->
<!-- - Herfindahl-Hirschman Index/HHI (Simpson) -->
<!-- - diversity decreasing for those still fishing in 2010, but not otherwise -->

<!-- ## @sethi2012b -->
<!-- - risk measures to 90 Alaskan fishing fishery/fleets -->
<!-- - revenue more variable than catch (+ price = extra variability) -->
<!-- - large catches, big fleets = lower risk -->

<!-- ## @sethi2010b -->
<!-- - risk management for fisheries review -->

<!-- ## @sethi2012 -->
<!-- - equal-share catch-pooling cooperatives in king and snow crab -->
<!-- - "variability reduction depends on the degree of correlation amongst -->
<!--   participants’ catches" -->

<!-- ## @sethi2014 -->
<!-- - community-level CFEC data -->
<!-- - number of fisheries strongest predictor of (lower) CV/CVaR -->
<!-- - also simpson index -->
<!-- - suggest barriers to commercial entry increase community risk by restricting -->
<!--   access to 'variety of fisheries' -->
<!-- - some communities have limited ability to diversify; may need to diversify -->
<!--   outside of fishing -->

<!-- [@perruso2005] -->
<!-- [@hilborn2001] -->
<!-- [@edwards2004] -->
<!-- [@trenkel2013] -->
<!-- [@mumford2009] -->
<!-- [@oostenbrugge2002] -->
<!-- [@baldursson1997] -->
<!-- [@jardine2015] -->
<!-- [@sanchirico2008] -->

<!-- vim: textwidth=80

-->

>>>>

@@

@@

@@

TODO: finish this:
External market forces may interact in concert with management regulations to
promote specialization for fishers or other individuals dependent on natural
resources. With increasing environmental variability and extreme events in
a changing climate (REF), it is particularly important that individuals who rely
on natural resources as a primary source of income have strategies to reduce
risk. Though variability in individual revenue may not be actively incorporated
into many management decisions, analyses like ours help to understand the range
of diversification strategies available and how their benefits may change over
time.

@@

<!-- vim: textwidth=80 -->
